																												% Thesis Preamable
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
                                          																			 % Packages																									%	
\documentclass[12pt]{article}																																															%
\usepackage{graphicx} 						  	 % Add pictures to your document																												%					
\usepackage{lscape}   								 % Use landscape in one page																														%
\usepackage{mfirstuc} 							   % Conatins Capitalize each word																												%
\usepackage{amsmath}                             % This is for math writing																															%
\usepackage[strings]{underscore}  			 % This is to recoginse the underscore																										%
\usepackage{apacite}                          		 % The citation package.																																%	
\usepackage[english]{babel} 					 % Use all English Language																														%
\setlength{\parindent}{2em}					     % Paragraph indent pakacge																														%
\usepackage{indentfirst}					    	 % To indent first paragraph of each section     																							%
\usepackage{cite}
\usepackage{natbib}								 	 % Gives different bib styles																														%																																																																									%																																																																									%																																																																									%																																																																									%																																																																									%																																																																									%
                                          																				 % Cover Page																							%
%\author{Ahmed F. Salhin}																																																	%
\title{Investor Sentiment and Stock Prices: Further Evidence from the UK}																							%
\date{\today{}}																																																					%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	\maketitle{}
	\pagenumbering{gobble}
	\pagenumbering{arabic}


\section{ABSTRACT} 


\section{Introduction}
\cite{Baker2007a} defined investor sentiment as “a belief about future cash flows and investment risks that is not justified by the facts at hand”. If investors base their investment decisions on this belief, asset prices will be driven away from their fundamental values. Prices then might be consistently over or underpriced as a result of the limited and costly arbitrage that would bring prices back to equilibrium. Investors sentiment can cost the market by increasing probability of bubbles occurrence. For example, Alan Greenspan, former chairman of the US Federal Reserve uses the term “Irrational Exuberance” to express his warning of the internet bubble. This link between investor irrtionality and financial crises is supported by \cite{Zouaoui2011} who show that the existence of investor sentiment increases the likelihood of stock market crises occurrence. 

\par Studies on investors irrationallity aim at invistigating the relationship between stock market returns and changes in invetor sentiment. While invistigating this relationship, these studies provides twofold benifits. The first is either the support or the creation of a measure of sentiment since investment sentiment is unobservabel. The second is the identfication of the relationship between investor sentiment and stock returns. Examples of these studies are \cite{Solt1988}, \cite{Lee1991, Abraham1993,Neal1998,Eichengreen1998,Fisher2000,Wang2003,Baker2006}

\section{Investor Sentiment and Financial markets}

\section{Data and Methodology}


\section{Findings}

\newpage

\bibliography{/Users/Ahmed/"Google Drive"/Apps/Tex/library.bib}
\bibliographystyle{apalike}

\end{document}